Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-11-02 PreregristrationS3/PreregistrationAOT-M.Rmd
equation first fix
pre-registration formulas ML corrected

---
title           : "Psychological Needs During Intergroup Contact: An Extensive Longitudinal Study (Young Medical Professionals Sample)"
shorttitle      : "Preregistration: Needs During Intergroup Contact"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name        : Jannis Kreienkamp
    affiliation : "1"
  - name        : Maximilian Agostini
    affiliation : "1"
  - name        : Laura Bringmann
    affiliation : "1"
  - name        : Peter de Jonge
    affiliation : "1"
  - name        : Kai Epstude
    affiliation : "1"
affiliation:
  - id          : 1
    institution : University of Groningen, Department of Psychology
bibliography: "../references.bib"
csl: apa.csl
biblio-style: "apalike" 
output: 
  prereg::cos_prereg:
    citation_package: natbib
editor_options: 
  chunk_output_type: console
---

@@

1. Contact Hypothesis (using between participant aggregates only to meaningfully include interaction frequency)
    a. Correlation: $r_{InteractionFrequency, OutgroupAttitudes} \neq 0$
    a. T-test: $\mu_{i,0utgroupInteraction} > \mu_{i,IngroupInteraction}$ (to build confidence in the persistence of the contact effect, we additionally compare the attitudes after an outgroup interaction to attitudes after no outgroup interaction (i.e., including instances where participants had no interaction at all).)
    a. Regression: $Attitude = ContactFreq \times AverageContactQual$
1. Allport's Conditions
    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}AllportConditions_{ti} + u_{0i} + u_{1i} + e_{ti}$
    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}AllportConditions_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + u_{1i} + e_{ti}$

        with $\begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix}$ and $e_{ti} \sim \mathcal{N}(0,\sigma^2)$
1. Key Need Fulfillment
    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}$
    a. Regression: $InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}$
    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + u_{1i} + e_{ti}$
    a. Regression: $Attitude_{ti} = KeyNeedFulfill_{ti} \times OutgroupInteraction_{ti} + u_{0i} + u_{1i} + e_{ti}$
    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + u_{1i} + e_{ti}$

        with $\begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix}$ and $e_{ti} \sim \mathcal{N}(0,\sigma^2)$
1. Comparison with Allport's Conditions
    a. Model Comparison: $AIC_{KeyNeedModel} > AIC_{AllportModel}$
    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}AllportConditions_{ti} + u_{0i} + u_{1i} + e_{ti}$

        with $\begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix}$ and $e_{ti} \sim \mathcal{N}(0,\sigma^2)$

>>>>

---
title           : "Psychological Needs During Intergroup Contact: An Extensive Longitudinal Study (Young Medical Professionals Sample)"
shorttitle      : "Preregistration: Needs During Intergroup Contact"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name        : Jannis Kreienkamp
    affiliation : "1"
  - name        : Maximilian Agostini
    affiliation : "1"
  - name        : Laura Bringmann
    affiliation : "1"
  - name        : Peter de Jonge
    affiliation : "1"
  - name        : Kai Epstude
    affiliation : "1"
affiliation:
  - id          : 1
    institution : University of Groningen, Department of Psychology
bibliography: "../references.bib"
csl: apa.csl
biblio-style: "apalike" 
output: 
  prereg::cos_prereg:
    citation_package: natbib
editor_options: 
  chunk_output_type: console
header-includes:
   - \usepackage{amsmath, nccmath}
---

@@

\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{0pt}
\setlength{\abovedisplayshortskip}{0pt}
\setlength{\belowdisplayshortskip}{0pt}

1. Contact Hypothesis (partially using between participant aggregates to meaningfully include interaction frequency)
    a. Correlation:
      \begin{fleqn}[\parindent] 
        \begin{equation}
          r_{ContactFreq, Attitude} \neq 0
        \end{equation}
      \end{fleqn}
    a. Regression:
        <!-- 
          Explanation: 
          - 'fleqn' aligns whole math left 
          - 'equation' adds number
          - 'split' aligns after level header
          - 'aligned[t]' aligns after equal sign
        -->
        \begin{fleqn}[\parindent] 
        \begin{equation}
          \begin{split}
            \textrm{Level 1:} &
              \begin{aligned}[t]
                \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}OutgroupInteraction_{ti} + \\
                                   &\ \beta_{2i}NonOutgroupInteraction_{ti} + e_{ti}
              \end{aligned} \\
            \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
                              &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
                              &\ \beta_{2i} = \gamma_{20} + u_{2i}
          \end{split} 
        \end{equation}
        \end{fleqn}
    a. Regression: 
      \begin{fleqn}[\parindent] 
        \begin{equation}
          Attitude = ContactFreq \times AverageQual
        \end{equation}
      \end{fleqn}
1. Allport's Conditions
    a. Regression:
        \begin{fleqn}[\parindent]
          \begin{equation} \label{eq:SlopesAttAllport}
            \begin{split}
                \textrm{Level 1:} &\ Attitude_{ti} = \beta_{0i} + \beta_{1i}AllportConditions_{ti} + e_{ti}\\
                \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
                                  &\ \beta_{1i} = \gamma_{10} + u_{1i}
            \end{split}
          \end{equation}
        \end{fleqn}
    a. Regression:
        \begin{fleqn}[\parindent]
          \begin{equation} \label{eq:SlopesQualAllport}
            \begin{split}
                \textrm{Level 1:} &\ InteractionQuality_{ti} = \beta_{0i} + \beta_{1i}AllportConditions_{ti} + e_{ti}\\
                \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
                                  &\ \beta_{1i} = \gamma_{10} + u_{1i}
            \end{split}
          \end{equation}
        \end{fleqn}
    a. Regression:
        \begin{fleqn}[\parindent]
          \begin{equation} \label{eq:SlopesAttAllportQual}
            \begin{split}
              \textrm{Level 1:} &
                \begin{aligned}[t]
                  \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}AllportConditions_{ti} + \\
                                     &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
                \end{aligned} \\
              \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
                                &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
                                &\ \beta_{2i} = \gamma_{20} + u_{2i}
            \end{split} 
          \end{equation}
        \end{fleqn}  
1. Key Need Fulfillment
    a. Regression: 
        \begin{fleqn}[\parindent]
          \begin{equation} \label{eq:SlopesAttCore}
            \begin{split}
                \textrm{Level 1:} &\ Attitude_{ti} = \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}\\
                \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
                                  &\ \beta_{1i} = \gamma_{10} + u_{1i}
            \end{split}
          \end{equation}
        \end{fleqn}
    a. Regression:
        \begin{fleqn}[\parindent]
          \begin{equation} \label{eq:SlopesQltCore}
            \begin{split}
                \textrm{Level 1:} &\ InteractionQuality_{ti} = \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}\\
                \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
                                  &\ \beta_{1i} = \gamma_{10} + u_{1i}
            \end{split}
          \end{equation}
        \end{fleqn}
    a. Regression:
        \begin{fleqn}[\parindent]
          \begin{equation} \label{eq:SlopesAttCoreQual}
            \begin{split}
              \textrm{Level 1:} &
                \begin{aligned}[t]
                  \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
                                     &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
                \end{aligned} \\
              \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
                                &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
                                &\ \beta_{2i} = \gamma_{20} + u_{2i}
            \end{split} 
          \end{equation}
        \end{fleqn}
    a. Regression: 
        \begin{fleqn}[\parindent]
          \begin{equation} \label{eq:SlopesAttCoreQualX}
            \begin{split}
              \textrm{Level 1:} &
                \begin{aligned}[t]
                  \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
                                     &\ \beta_{2i}InteractionQuality_{ti} + \\
                                     &\ \beta_{3i}KeyNeedFulfill*InteractionQuality_{ti} + e_{ti}
                \end{aligned} \\
              \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
                                &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
                                &\ \beta_{2i} = \gamma_{20} + u_{2i} \\
                                &\ \beta_{3i} = \gamma_{30} + u_{3i}
            \end{split} 
          \end{equation}
        \end{fleqn}
    a. Regression: 
        \begin{fleqn}[\parindent]
          \begin{equation} \label{eq:SlopesAttCoreSdt}
            \begin{split}
              \textrm{Level 1:} &
                \begin{aligned}[t]
                  \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \beta_{2i}Autonomy_{ti} + \\
                                     &\ \beta_{3i}Competence_{ti} + \beta_{4i}Relatedness_{ti} + e_{ti}
                \end{aligned} \\
              \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
                                &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
                                &\ \beta_{2i} = \gamma_{20} + u_{2i} \\
                                &\ \beta_{3i} = \gamma_{30} + u_{3i} \\
                                &\ \beta_{4i} = \gamma_{40} + u_{4i}
            \end{split} 
          \end{equation}
        \end{fleqn}
1. Comparison with Allport's Conditions
    a. Model Comparison:
      \begin{fleqn}[\parindent] 
        \begin{equation}
          AIC_{KeyNeedModel} < AIC_{AllportModel}
        \end{equation}
      \end{fleqn}
    a. Regression: 
        \begin{fleqn}[\parindent]
          \begin{equation} \label{eq:SlopesAttCoreAllport}
            \begin{split}
              \textrm{Level 1:} &
                \begin{aligned}[t]
                  \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
                                     &\ \beta_{2i}AllportConditions_{ti} + e_{ti}
                \end{aligned} \\
              \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
                                &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
                                &\ \beta_{2i} = \gamma_{20} + u_{2i}
            \end{split} 
          \end{equation}
        \end{fleqn}

All multilevel assumptions are tested as usual including (e.g., for random slopes model with _j_ within person predictors):

\begin{flalign}
  &\textrm{Level 1 Variance:}\ e_{ti} \sim \mathcal{N}(0,\sigma^2) \\
  &\textrm{Level 2 Variance:}\ \begin{bmatrix} u_{0i}\\ \vdots\\ u_{ji}\end{bmatrix} 
  \sim \mathcal{N}
  \begin{pmatrix}
    \begin{bmatrix} 
      0 \\ 
      \vdots \\
      0
    \end{bmatrix}, 
    \begin{bmatrix} 
      \tau_{00}^2 &  & \\ 
      \vdots & \ddots & \\
      \tau_{j0} & \ldots & \tau_{jj}^2
    \end{bmatrix}
  \end{pmatrix}
\end{flalign}
